---
title: "p8105_hw6_jkl2195"
author: "Jessie Li"
date: "2023-11-30"
output: github_document
---
Import libraries
```{r}
library(tidyverse)
library(readr)
library(modelr)
library(mgcv)

```

# Problem 1
```{r}
homicide_df = read_csv("data/homicide-data.csv") |>
  mutate(
    city_state = str_c(city, ", ", state),
    solved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"),0,1),
    victim_age = as.numeric(victim_age)
  ) |>
  select(-city, -state) |>
  filter(
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black"),
    !is.na(victim_age)
  ) |>
  rename_with(.fn = ~ (gsub("victim_", "", .x, fixed = TRUE)), .col = starts_with("victim_"))

```

Created a city_state variable that combines city and state variables, and a binary variable indicating whether the homicide is solved (1 for solved, 0 for unsolved). Omited cities Dallas, TX; Phoenix, AZ; and Kansas City, which didn’t report victim race. Tulsa, AL is dropped due to a data entry mistake. We only focus on white and black race with the highest data entries. Invalid age are dropped from the dataset.

```{r}
solved_glm_obj = homicide_df |>
  filter(city_state == "Baltimore, MD") |>
  glm(solved ~ age + sex + race, family = binomial(), data = _)

solved_glm = solved_glm_obj |>
  broom::tidy() |>
  mutate(
    OR = exp(estimate),
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)
  ) |> 
  filter(term == "sexMale") |> 
  select(OR, OR_CI_lower, OR_CI_upper)

solved_glm
```


For the city of Baltimore, MD, used the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. The odds ratio and its confidence interval are given above.

```{r}
solved_city_glm = homicide_df |>
  nest(data = -city_state) |>
  mutate(
    model = map(data, \(df)glm(solved ~ age + sex + race, family = binomial(), data = df)),
    result = map(model, broom::tidy)
  ) |>
  unnest(result) |>
  select(-model,-data) |>
  mutate(
    OR = exp(estimate),
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)
  ) |>
  filter(term == "sexMale")

solved_city_glm
```


Applied glm to the entire dataset by nesting. The confidence interval of the estimation is also given above.

```{r}
solved_city_glm |>
  ggplot(aes(x = fct_reorder(city_state, OR), y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

This is a plot that shows the estimated ORs and CIs for each city, which is ordered according to estimated OR.For the cities with higher adjusted odds ratio, the confidence interval is larger. Most of the cities has a confidence interval below one.


# Problem 2


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
Import weather data using code provided by P8105.

```{r}
z_value = qnorm(.975)
tmax_boot_straps = weather_df |>
  mutate(
    strap_sample = map(id, \(i) sample_n(weather_df, size = 5000, replace = TRUE)),
    model = map(strap_sample, \(sample) lm(tmax ~ tmin + prcp, data = sample)),
    result = map(model, broom::tidy),
    glan = map(model, broom::glance)
  ) |>
  unnest(result, glan) |>
  select(date, term, estimate, r.squared) |>
  pivot_wider(
    names_from = term,
    values_from = estimate) |>
  mutate(
      log_product = log(tmin * prcp)
    )

r_square_CI_lower = tmax_boot_straps |> pull(r.squared) |> quantile(.025)
r_square_CI_upper = tmax_boot_straps |> pull(r.squared) |> quantile(.975)

log_CI_lower = tmax_boot_straps |> na.omit(log_product) |> pull(log_product) |> quantile(.025)
log_CI_upper = tmax_boot_straps |> na.omit(log_product) |> pull(log_product) |> quantile(.975)
```
Used bootstrap 5000 times to create 5000 linear models. The model predicted maximum temperature using the minimum temperature and precipation as predictors. Out of the 5000 model, the 95% confidence interval of R square is (`r r_square_CI_lower`, `r r_square_CI_upper`), and the 95% confidence interval of log of the product of two coefficients is (`r log_CI_lower`, `r log_CI_upper`). The following shows the plots of R square and log product of coefficients of the bootstrap samples.

```{r}
tmax_boot_straps |>
  ggplot(aes(x = r.squared)) +
  geom_density()

tmax_boot_straps |>
  na.omit(log_product) |>
  ggplot(aes(x = log_product)) +
  geom_density()
```
The plot for r square shows approximately normal distribution with mean around 0.916, validating the model as it is almost 1. The plot for the log product shows a right skewed distribution with median between -8 and -7.

# Problem 3

```{r}
birth_df = read_csv("data/birthweight.csv") |>
  na.omit() |>
  mutate(
    babysex = recode(babysex, `1` = "male", `2` = "female"),
    babysex = factor(babysex),
    frace = recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    frace = factor(frace),
    mrace = recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    mrace = factor(mrace),
    malform = recode(malform, `0` = "absent", `1` = "present"),
    malform = factor(malform)
  )

```

Loaded and cleaned the birth weight data. This dataset contains 4342 observations and 20 variables. Notable variables includes baby's birth weight, race of the parents, mother's weight, previous history of births, baby's head circumference and smoking status. The categorical variables such as baby's sex, parent's race, etc. is recoded and factored to the corresponding value. NA values are dropped from the dataset.


```{r}
full_model = lm(bwt ~., data = birth_df)
models = c()
predictor_list = data_frame(predictor = character(), p_value = double(), id = integer())
predictor = birth_df |>
  select(-bwt) |>
  colnames()

# Forward Selection
join_predictors = function(predictor_list){
  string = ''
  for(i in predictor_list){
    if(string == ''){
      string = str_c(i, " + ")
    } else{
      string = str_c(string, i, " + ")
    }
  }
  return(string)
}


generate_predictors = function(dependent, predictor_list, model_df, data_df, iter){
  value = model_df |>
    filter(length(predictor_list |> pull(predictor)) == 0 |
             !(predictor %in%  pull(predictor_list, predictor))) |>
    mutate(
      model = 
        map(predictor, \(col) paste(dependent, 
                                     ' ~ ', 
                                     predictor_list |>
                                       pull(predictor) |>
                                       join_predictors(),
                                     col)) |>
        map(as.formula) |>
        map(lm, data = data_df),
      results = map(model, broom::glance)
    ) |>
    unnest(results) |>
    na.omit(p.value) |>
    filter(p.value != 0) |>
    filter(p.value == min(p.value)) |>
    select(predictor, model, p.value)
  bind_rows(predictor_list, data_frame(predictor = value |> pull(predictor), 
                                       model = value |> pull(model),
                                       p_value = value |> pull(p.value), 
                                       id = iter))
}

model_df = predictor |>
  data_frame()

for(i in 1:4){
  predictor_list = generate_predictors(dependent = 'bwt', predictor_list, model_df, data_df = birth_df, i)
}

#lm(btw ~ Bloodclot, data = surg)
#summary(fit1)
```

By forward selection process of 4 variables, we have selected the following predictors: `r paste(pull(predictor_list, predictor)). The forward selection stops when it reaches 4 variables. For each time, the variable is selected and tested for the most significant p.value. Then the variable is added to model and test for the next variable.

```{r}
final_model = predictor_list |>
  filter(id == max(id)) |>
  pull(model) |>
  nth(1)

pred = modelr::add_predictions(data = birth_df, model = final_model)
pred = modelr::add_residuals(data = pred, model = final_model)

pred |>
  ggplot(aes(y = resid, x = pred)) +
  geom_point()
```
The above plot depicts a relationship between residuals and prediction of the linear model. Ideally, the scores should be randomly distributed on both sides of residual = 0. This case, the points are evenly spread on both sides of the axis, but it seems to have a concentration around residual = 0 and prediction = 3000.

```{r}
cv_df = 
  crossv_mc(birth_df, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) |>
  mutate(
    my_lm = map(train, \(df) lm(bwt ~ gaweeks + delwt + mrace + ppbmi, data = df)),
    length_gest_lm = map(train, \(df) lm(bwt ~ blength + gaweeks, data = birth_df)),
    cir_length_sex_lm = map(train, \(df) lm(bwt ~ bhead + blength + babysex + bhead * blength + blength * babysex + bhead * babysex + bhead * blength * babysex, data = birth_df)),
    rmse_my = map2_dbl(my_lm, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_length_gest = map2_dbl(length_gest_lm, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_cir_length_sex = map2_dbl(cir_length_sex_lm, test, \(mod, df) rmse(model = mod, data = df))
  )

cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


We tested our model against two other proposed models given by P8105:
 - (Model 2) One using length at birth and gestational age as predictors (main effects only)
 - (Model 3) One using head circumference, length, sex, and all interactions (including the three-way interaction) 

Model 3 has the best root mean squared error compared to all other models with range between 250 and 325. This is followed by model 2 with range 300 and 375. My model has a root square mean error between  400 and 475. This could be due to lack of interacting term in my model.
